Nour Al Afif

### 2023-08-29 team/senior/mikayla-lalli.qmd
reinit to new quarto version

---
title: "Mikayla Lalli"
subtitle: "M.Sc. Candidate"
image: mikayla-lalli.jpg
sortby: 2
started: "September 2022"
about:
  id: hero-heading
  template: solana
  links:
    - icon: github
      text: github
      href: https://www.github.com/mikaylalalli
---

>>>>

---
title: "Mikayla Lalli"
subtitle: "M.Sc. Candidate"
image: mikayla-lalli.jpg
sortby: 3
started: "September 2022"
about:
  id: hero-heading
  template: solana
  links:
    - icon: github
      text: github
      href: https://www.github.com/mikaylalalli
---

### 2023-08-29 team/senior/nour-alafif.qmd
reinit to new quarto version

---
title: "Nour Al Afif"
subtitle: "M.Sc. Candidate"
image: nour-alafif.jpg
sortby: 3
started: "September 2022"
about:
  id: hero-heading
  template: solana
  links:
    - icon: github
      text: github
      href: https://www.github.com/NourAlAfif19
---

>>>>

---
title: "Nour Al Afif"
subtitle: "M.Sc. Candidate"
image: nour-alafif.jpg
sortby: 4
started: "September 2022"
about:
  id: hero-heading
  template: solana
  links:
    - icon: github
      text: github
      href: https://www.github.com/NourAlAfif19
---
